Handling String-Number Conversion in String Constraint Solving

### 2019-11-13 draft.tex
polish a bit intro and under-approximation

	 	\caption{Encoding \texttt{Split(x,y)} using recursive functions and the array theory. The recursive function \texttt{split (x y 0 0)} returns an array of type \texttt{(Array Int String)} that maps an index $i$ to the $i$th component (separated by the character $y$ ) of $x$.}
	 	\label{fig:smt_string}
\end{figure}

@@

\section{Under-approximation} \label{section:under_approximate}
In this section, we describe formally how to restrict the domain of string variables to patterns defined by \emph{parametric flat automata} (PFA) (Section~\ref{section:sfa}) and hence convert string constraints $\phi_s$ to a set of equisatisfiable linear integer constraints $\phi_I$ in polynomial-time. We first pick a PFA for each variable in $\vars$ and then construct the set of linear integer constraints in a stepwise manner. In each step, we take a string constraint from $\phi_s$ and depending on the type of the string constraint, we execute the corresponding procedure to produce the linear integer constraints. The procedure for equality, disequality, and membership constraints is in Section~\ref{section:eq} and the one for string-number conversion is in Section~\ref{section:s2i}.

@@

\subsection{Flat Under-approximation for Equalities and Regular Constraints} \label{section:eq}

@@

Disequality constraint $x_1\cdot x_2 \cdots x_n \neq x_{n+1}\cdot x_{n+2} \cdots x_m$ can be converted to equal-satisfiable equality constraints in the standard way~\cite{abdulla2015norn}. We replace it with the following constraints.

The second disjunct says that the constraints $x_1\cdot x_2 \cdots x_n$ and $x_{n+1}\cdot x_{n+2} \cdots x_m$ have a common prefix $y_1$, but the next character $y_2$ and $y'_2$ is different. In an more efficient implementation, one just project $y_2$ and $y'_2$ to a PFA that accept only symbolic words $v_1$ and $v'_1$, respectively (the PFA has no loop and only one transition).

>>>>

	 	\caption{Encoding \texttt{Split(x,y)} to an SMTLIB2 formula using recursive functions and the array theory. The recursive function \texttt{split (x y 0 0)} returns an array of type \texttt{(Array Int String)} that maps an index $i$ to the $i$th component (separated by the character $y$ ) of $x$.}
	 	\label{fig:smt_string}
\end{figure}

@@

\section{Under-approximation} \label{section:under_approximate}
In this section, we describe formally how to restrict the domain of string variables to patterns defined by \emph{parametric flat automata} (PFA) (Section~\ref{section:sfa}) and hence convert string constraints $\phi_I$ to a set of equisatisfiable linear formulas $\phi_O$ in polynomial-time. We assume all disequality constraint $t_1 \neq t2 \in \phi_d$ are already converted to equal-satisfiable equality constraints and integer constraints in the standard way~\cite{abdulla2015norn}.

We pick a PFA for each variable in $\vars$ at the beginning of the decision procedure and then construct the set of linear integer constraints in a stepwise manner. In each step, we take a string constraint from $\phi_I$ and depending on the type of the string constraint, we execute the corresponding procedure to produce the linear integer constraints and add them to the output linear formulas $\phi_O$.

More concretely, at the beginning, we move all integer constraints in $\phi_I$ to the output linear formulas $\phi_O$. After this step, $\phi_I$ is the union of the three sets of constraints $\phi_e$ (equality), $\phi_m$ (membership), and $\phi_s$ (string-number conversion). For all string variables $x$ that occurs in a string-number conversion constraint $n= \sti{x} \in \phi_s$, we follow the rule that will be described in Section~\ref{section:s2i} to pick the corresponding PFA and we do not set any restriction to the selection of PFA for other string variables, i.e., the selection is an implementation decision. We will describe the PFA selection strategy of \tool in Section~\ref{section:implementation}.

After the PFA for each variable is selected, we step-wisely pick and remove a string constraint from $\phi_I$, executing the corresponding procedure to create equisatisfiable linear constraints, and add all the results to $\phi_O$. The procedure for equality and membership constraints is in Section~\ref{section:eq} and the one for string-number conversion is in Section~\ref{section:s2i}.

\hide{We replace it with the following constraints.

	The second disjunct says that the constraints $x_1\cdot x_2 \cdots x_n$ and $x_{n+1}\cdot x_{n+2} \cdots x_m$ have a common prefix $y_1$, but the next character $y_2$ and $y'_2$ is different. In an more efficient implementation, one just project $y_2$ and $y'_2$ to a PFA that accept only symbolic words $v_1$ and $v'_1$, respectively (the PFA has no loop and only one transition). }

@@

\subsection{Handling Equalities and Regular Constraints Symbolically} \label{section:eq}

@@
